Issues with Dynamical Measurements Across the Disk

### 2019-02-26 paper/ms.tex
Change to prevent overrunning margin

\section{Azimuthal midplane variations at the Solar Circle: estimates from
FIRE} \label{sec:local_fire}
\subsection{Description of Simulation} \label{ssec:cosmozoom}
Here we briefly describe the cosmological-hydrodynamical zoom-in simulations
used in this work. Cosmological zoom-ins allow one to simulate a selected
region at high resolution embedded in a low-resolution cosmological background
\citep[e.g.][]{1993ApJ...412..455K,2014MNRAS.437.1894O}, to which can be added
a hydrodynamical simulation of the baryonic component with recipes for star
formation and feedback. The FIRE collaboration has simulated a number of Milky
Way-mass galaxies using this technique as part of the {\em Latte} suite of
FIRE-2 simulations \citep{2016ApJ...827L..23W,2018MNRAS.481.4133G}. For this
work we focus on the three zoom-ins considered in \citet{2018arXiv180610564S},
which show broad agreement of many of their global properties with
observations of the Milky Way. The $\z=0$ snapshots\footnote{In this work, to
avoid confusion with the vertical height $z$, we refer to cosmological
redshift as $\z$.} of these three simulations, called \mi , \mf , and \mm{}
for shorthand, are publicly available alongside associated mock {\em Gaia} DR2
catalogues generated from them.\footnote{at \url{http://ananke.hub.yt}}

>>>>

\section{Azimuthal midplane variations at the Solar Circle: estimates from
FIRE} \label{sec:local_fire}
\subsection{Description of Simulation} \label{ssec:cosmozoom}
We briefly describe the cosmological-hydrodynamical zoom-in simulations used
in this work. Cosmological zoom-ins allow one to simulate a selected region at
high resolution embedded in a low-resolution cosmological background
\citep[e.g.][]{1993ApJ...412..455K,2014MNRAS.437.1894O}, to which can be added
a hydrodynamical simulation of the baryonic component with recipes for star
formation and feedback. The FIRE collaboration has simulated a number of Milky
Way-mass galaxies using this technique as part of the {\em Latte} suite of
FIRE-2 simulations \citep{2016ApJ...827L..23W,2018MNRAS.481.4133G}. For this
work we focus on the three zoom-ins considered in \citet{2018arXiv180610564S},
which show broad agreement of many of their global properties with
observations of the Milky Way. The $\z=0$ snapshots\footnote{In this work, to
avoid confusion with the vertical height $z$, we refer to cosmological
redshift as $\z$.} of these three simulations, called \mi , \mf , and \mm{}
for shorthand, are publicly available alongside associated mock {\em Gaia} DR2
catalogues generated from them.\footnote{at \url{http://ananke.hub.yt}}
